% Cover letter using letter.cls
\documentclass{letter} % Uses 10pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8.5in    % text height can be bigger for a longer letter
\oddsidemargin=0pt   % leftmargin is 1 inch
\textwidth=6.5in     % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Thomas M. Rodriguez}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter}{
Hiring Manager \\
Nextiva \\
Scottsdale, AZ}

\begin{center}
{\large\bf Thomas M. Rodriguez}
\end{center}
\medskip\hrule height 1pt
\begin{center}
{2781 W Anklam Unit F \\ Tucson, AZ 85745 \\ (619) 248-0717}
\end{center} \vfill % forces letterhead to top of page
 
 
\opening{Dear Hiring Manager:}
 
% \noindent PARAGRAPH ONE: State reason for letter, name the position or type 
% of work you are applying for and identify source from  which  you 
% learned   of   the  opening.  (i.e.  Career  Development  Center, 
% newspaper, employment service, personal contact). 

\noindent I am writing this letter for a chance to interview for the position of Front End Developer.
 
% \noindent PARAGRAPH  TWO:  Indicate why you are interested in the position, 
% the company, its products, services - above all, stress what  you 
% can  do  for  the employer. If you are a recent graduate, explain 
% how your academic background makes you a qualified candidate  for 
% the  position.  If  you have practical work experience, point out 
% specific achievements or unique qualifications. Try not to repeat 
% the  same  information  the reader will find in the resume. Refer 
% the reader to the enclosed resume or application which summarizes 
% your  qualifications,  training,  and experiences. The purpose of 
% this section is to strengthen your resume  by  providing  details 
% which bring your experiences to life. 

\noindent I have experience with Postgresql after using it with most of my Backend projects.  I also completed Stanford's Relational Algebra Course giving me a better understanding of Structured Query Language.  I have written several ruby scripts to accomplish tasks ranging from web scraping, calculating the Fibonacci sequence to many places, as well as utilizing Fermat's factorization method to factor large integers.  I have built several server side projects using Ruby on Rails including a twitter clone, and Django, building a basic eCommerce site as well as a portfolio site utilizing Mezzanine CMS.  I have a strong understanding of the Javascript language building a jQuery Etch-a-Sketch, and using it to calculate the Fibonacci sequence to many places as well as implementing Fermat's factorization method.  I prefer to use coffeescript and it fits in my Static Site Development stack when I write jQuery.  I am well aware of the power of modern HTML5/CSS3 and have used gradients, border-radius', and other convenient additions to keep my sites current.  I opt to use git as much as possible and I have even pushed up this cover letter as a tex file and PDF (now viewable on github) to my repository at https://github.com/trodrigu/resume/blob/master/cover\_let.pdf.  I have used Application Programming Interfaces for an assortment of things including using Google's Calendar API to aid in the scheduling of Google Ads with javascript or using Stripe's API for payment processing in my Django project.
 
% \noindent PARAGRAPH THREE: Request a personal interview and  indicate  your 
% flexibility as to the time and place. Repeat your phone number in 
% the letter and offer assistance to help in a speedy response. For 
% example,  state that you will be in the city where the company is 
% located on a certain date and would like to set up an  interview. 
% Or,  state  that  you  will  call  on a certain date to set up an 
% interview. End the letter by thanking  the  employer  for  taking 
% time to consider your credentials. 

\noindent At the moment I am working full time, however, I am capable of scheduling an interview within a weeks notice because of the ability to work from home.  My phone number is (619)-248-0717.  Thank you for taking the time to consider my credentials.
 
\closing{Sincerely yours,} 
 

 
% \encl{}					% Enclosures

\end{letter}
 

\end{document}
